---
title: "Final_project_work3"
author: "Ninna Nataly Iriondo Castro Friis"
date: "2022-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#I load the different library packages, so I can use the tools
```{r}
library(tidyverse)
library(here)
library(dplyr)
library(tidytext)
library(pdftools)
library(readxl)
```

#I make a vector with list of the dataset from 1371-1400 and name it "filnavne"
```{r}
list.files("Data_1371_1400", full.names = TRUE) -> filnavne
```

#Combine the dataset from 1371 to 1998, because the dataset from 1999-1400 do not contain the letters that I can use, I will not combine it - The name will still be 1371-1400, because it does it a lot easier
```{r}
DRB_1371_1400 <- tibble()
tmp_df <- tibble()
fil <- c()
for (fil in filnavne){
  print(fil)
  tmp_df <- read_excel(fil)
  tmp_df <- tmp_df %>% 
    mutate(Nummer= as.numeric(Nummer))
  DRB_1371_1400 <- bind_rows(DRB_1371_1400, tmp_df)
}
```

#Convert the raw dataset from excel fil to csv and import to Jupyter Lab to extract the names
```{r}
DRB_1367_1370.csv <- read_csv2("Data_1367_1370/Datasæt_DRB_1367_1370.xlsx")
```
#Read the 1367-1370_name csv files in R, which is importet from Jupyter Lab
```{r}
DRB_1367_1370_name <- read_csv2("Data/DRB_1367_1370_name.csv")
```
#split the column ",doc_id,name" to 3 seperated columns
```{r}
DRB_1367_1370_name[c('number', 'doc_id', 'name')] <- str_split_fixed(DRB_1367_1370_name$",doc_id,name", ',', 3)
```


#Split the text in the column "name" into words using to tokens function
```{r}
DRB_tokens1 <- DRB_1367_1370_name %>% 
  unnest_tokens(word, ",doc_id,name")
```

#Create a stopwordlist and make it a dataframe
```{r}
stop_words1 <- tibble(word=c("Gud","Guds","Margrete","Valdemar","Eder","'","Eders","eder","eders","margrete","margretes","valdemar","gud","guds", "oluf","v","van","Erik","erik"))
```

#Remove the stopwordlist from the wordlist "DRB_tokens1"
```{r}
DRB_stop1 <- DRB_tokens1 %>%
  anti_join(stop_words1)
```

#count the names and look which 10 names occur most often
```{r}
DRB_1367_1370_names_count <- DRB_stop1 %>% 
  count(word, sort = TRUE) %>% 
  head(10) 
```

#rename the column "word" to "name"
```{r}
names(DRB_1367_1370_names_count)[names(DRB_1367_1370_names_count)=="word"] <- "name"
```


#Put the 10 names into a ggplot with geom columns, reorder it and color it
```{r}
ggplot(data = DRB_1367_1370_names_count, aes(x = reorder(name, -n), y = n, color=name, fill=name))+
  geom_col() +
  labs(x="name")

```

#Read the csv file from 1371_1400_name from Jupyter Lab into R
```{r}
DRB_1371_1400_names <- read.csv("Data/DRB_1371_1400_name.csv")
```

#split the text in the column "name" into words
```{r}
DRB_tokens2 <- DRB_1371_1400_names %>% 
  unnest_tokens(word, name)
```
#I use the same stopwordlist

#remove the stopwordlist from the wordlist "DRB_tokens2"
```{r}
DRB_stop2 <- DRB_tokens2 %>%
  anti_join(stop_words1)
```

#count the names and look which 10 names occur most often
```{r}
DRB_1371_1400_names_count <- DRB_stop2 %>% 
  count(word, sort = TRUE) %>% 
  head(10)
```

#rename the column "word" to "name"
```{r}
names(DRB_1371_1400_names_count)[names(DRB_1371_1400_names_count)=="word"] <- "name"
```


#Put the 10 names into a ggplot with geom columns, color it and reorder it
```{r}
ggplot(data = DRB_1371_1400_names_count, aes(x = reorder(name, -n), y = n, color=name, fill=name))+
  geom_col() +
  labs(x="name")
  
```

